Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-04-04 submission/Sze_Obesity_PeerJ_2016.Rmd
Work with YAML header material

---
title: "Looking for a Signal in the Noise: Revisiting Obesity and the microbiome"
output:
  html_document:
    keep_md: yes
  word_document:
    reference_docx: manuscript_template.docx
bibliography: metaAnalysis.obesity.microbiome.bib
---

>>>>

---
title: "Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome"
output:
  html_document:
    keep_md: yes
bibliography: submission/references.bib
---

### 2016-04-04 submission/Sze_Obesity_PeerJ_2016_Supp.Rmd
Work with YAML header material

---
title: "Bacterial Microbiome and Obesity Meta-analysis Supplemental"
author: "Marc Sze"
date: "January 26, 2016"
output:
  html_document:
    keep_md: yes
bibliography: metaAnalysis.obesity.microbiome.bib
---
<br><br>

>>>>

---
title: "Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome"
output:
  html_document:
    keep_md: yes
bibliography: submission/references.bib
---

Marc A Sze<sup>1</sup> and Patrick D Schloss<sup>1</sup>
